MixEth: efficient, trustless coin mixing service for Ethereum

### 2018-11-26 article/main.tex
Updated acknowledgements

\section{Future work}
We are going to implement and deploy MixEth on Ethereum and evaluate its performance. We are also going to give formal security proofs for the claimed security properties.  
An important and crucial research question is whether it is possible to design and implement an efficient and trustless Ethereum-based coin mixer with strong security guarantees which do not rely on any workaround and upcoming EIP implementation and is ready to be deployed on present-day Ethereum.

\section{Acknowledgements}
We would like to thank Liam Horne, barryWhiteHat, Dmitry Khovratovich and Sina Mahmoodi for the insightful comments and discussions.

>>>>

\section{Future work}
We are going to conduct external code audits, deploy MixEth on the Ethereum main net and evaluate its performance. An important and crucial research question is whether it is possible to design and implement an efficient and trustless Ethereum-based coin mixer with strong security guarantees which do not rely on any workaround or upcoming EIP implementation and is ready to be deployed on present-day Ethereum.

\section{Acknowledgements}
Chris Buckland is supported by an Ethereum Foundation
scaling grant and an Ethereum Community Fund grant.
We would like to thank Liam Horne, Patrick McCorry, barryWhiteHat, Dmitry Khovratovich and Sina Mahmoodi for the insightful comments and discussions.
